Arbeidskrav våren 2022

### 2022-01-13 MSB106_Arbeidskrav_V22_Backup.Rmd
Fiksa glømt innlesing

```{r csv_filer}
syssel_arb <- read_csv("Data/syssel_arb.csv", show_col_types = FALSE)
hld_arb <- read_csv("Data/hld_arb.csv", show_col_types = FALSE)
sun_arb <- read_csv("Data/sun_arb.csv", show_col_types = FALSE)
har_arb <- read_csv("Data/har_arb.csv", show_col_types = FALSE)
syssel_bos <- read_csv("Data/syssel_bos.csv", show_col_types = FALSE)
hld_bos <- read_csv("Data/hld_bos.csv", show_col_types = FALSE)
sun_bos <- read_csv("Data/sun_bos.csv", show_col_types = FALSE)
har_bos <- read_csv("Data/har_bos.csv", show_col_types = FALSE)
Pendling <- read_csv("Data/Pendling.csv", show_col_types = FALSE)
hgl_Pendling <- read_csv("Data/hgl_Pendling.csv", show_col_types = FALSE)
sun_Pendling <- read_csv("Data/sun_Pendling.csv", show_col_types = FALSE)
hld_bos_LQ <- read_csv("Data/hld_bos_LQ.csv", show_col_types = FALSE)
sun_bos_LQ <- read_csv("Data/sun_bos_LQ.csv", show_col_types = FALSE)
```

>>>>

```{r csv_filer}
syssel_arb <- read_csv("Data/syssel_arb.csv", show_col_types = FALSE)
hld_arb <- read_csv("Data/hld_arb.csv", show_col_types = FALSE)
sun_arb <- read_csv("Data/sun_arb.csv", show_col_types = FALSE)
har_arb <- read_csv("Data/har_arb.csv", show_col_types = FALSE)
syssel_bos <- read_csv("Data/syssel_bos.csv", show_col_types = FALSE)
hld_bos <- read_csv("Data/hld_bos.csv", show_col_types = FALSE)
sun_bos <- read_csv("Data/sun_bos.csv", show_col_types = FALSE)
har_bos <- read_csv("Data/har_bos.csv", show_col_types = FALSE)
Pendling <- read_csv("Data/Pendling.csv", show_col_types = FALSE)
hgl_Pendling <- read_csv("Data/hgl_Pendling.csv", show_col_types = FALSE)
sun_Pendling <- read_csv("Data/sun_Pendling.csv", show_col_types = FALSE)
hld_bos_LQ <- read_csv("Data/hld_bos_LQ.csv", show_col_types = FALSE)
sun_bos_LQ <- read_csv("Data/sun_bos_LQ.csv", show_col_types = FALSE)
har_bos_LQ <- read_csv("Data/hld_bos_LQ.csv", show_col_types = FALSE)
```
